Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-09-29 main.tex
stuff

\subsection{\cye{A triangulation or a simplicial complex}}

@@

A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation} if it satisfies the following conditions: 
(i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
% (i) every subsimplex of any simplex in $\calT$ is itself part of $\calT$, and (ii) the intersection between any two simplices $T, T' \in \calT$ is either empty or a shared subsimplex of both $T$ and $T'$. 
We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\todo{MV: Don't we only use $n$-dimensional simplicial complexes? That would be a simplification of our presentation.}\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) \cye{and simply ``simplicial meshes'' in the finite element literature}.} 
We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is \sout{defined as} the union 
\begin{align*}
    \underlying{\calT} := \bigcup_{ T \in \calT } T
    .
\end{align*}
We call any set triangulable if it is the underlying set of some triangulation. 
\\

@@

We introduce a specific notion of connectivity when we are given an $n$-dimensional simplicial complex $\calT$. 
We call two $n$-dimensional simplices $S, S' \in \calT$ \emph{face-neighboring} if $S \cap S'$ is a common face of both of them. 
We call $n$-simplices $S,S' \in \calT$ \emph{face-connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$. % TODO: Theo suggests reverse order of that sequence 
We call such a sequence a \emph{strong path} from $S$ to $S'$ in $\calT$. \mwl{Change the terminology strong path to something else.}
Clearly, face-connected in $\calT$ is an equivalence relation among simplices. 
A \emph{face-connected component} of $\calT$ is an equivalence class under this equivalence relation, 
and we call $\calT$ \emph{face-connected} if it has only one face-connected component.

\mwl{We should use clarify face vs facet}

@@

\mwl{Throughout the manuscript, use a macro for opnorm and equip the matrices with the operator norm index.}

@@

We are interested in transformations of Sobolev tensor fields from one domain onto \cye{an}other. 
Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
The pullback of $u \in W^{p}\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
\begin{align} \label{equation:pullback}
    \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
    := 
    u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
\end{align}
for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^{p}\Alt^{k}(\Omega)$.
We cite an explicit transformation estimate~\cite{licht2019smoothed}.

\begin{proposition} \label{proposition:pullbackestimate}
 Let $\phi : \Omega \rightarrow \Omega'$ be a bi-Lipschitz mapping between open sets $\Omega, \Omega' \subseteq \bbR^{n}$.
 Let $p \in [1,\infty]$ and $u \in L^{p}\Lambda^{k}(\Omega)$. 
 Then 
 \begin{align}\label{math:pullbackestimate}
  \begin{split}
  \| \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}
  &\leq 
  \| \Jacobian \phi \|^{k}_{L^{\cye{\infty}}(\Omega)}
  \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\cye{\infty}}(\Omega')}
  \| u \|_{L^{p}\Lambda^{k}(\Omega')}
  .
  \end{split}
 \end{align}
\end{proposition}
\notice{MWL:I have simplified the statement to what is needed later.}

@@

{\color{red}
We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
We already know the optimal constants for the gradient operator over convex domains,
and we know bounds for the Poincar\'e--Friedrichs constants for the entire $L^{2}$ de~Rham complex. 
We are not aware of such bounds for the case of the $L^{p}$ de~Rham complex when $1 \leq p \leq \infty$.

For that reason, we bound the norms of regularized potential operators for the exterior derivative over convex domains.
We solve this for two special cases: either the $L^{p}$ de~Rham complex without boundary conditions, 
and the $L^{p}$ de~Rham with full boundary conditions. 
The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
who analyze them as pseudodifferential operators over domains star-shaped with respect to a ball. 
% 
In comparison to their work, our discussion is more modest:
we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
However, our purpose are explicit bounds for the operator norms, which are of independent interest.

In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.
}

We \cye{now give} bounds for Poincar\'e--Friedrichs constants for the exterior derivative over convex domains\cye{, in} two special cases\todo{MV: Discussion already in the introduction, or in Remark~\ref{remark:reg_Poinc_Bog}}: 
either the $L^{p}$ de~Rham complex without boundary conditions, \cye{or} the $L^{p}$ de~Rham with full boundary conditions. 
The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
who analyze them as pseudo\cye{-}differential operators over domains star-shaped with respect to a ball. 
In comparison to their work, our discussion is more modest:
we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
However, our purpose are explicit bounds for the operator norms, \cye{giving the Poincar\'e--Friedrichs constants}. Let $\Omega \subseteq \bbR^{n}$ is a convex bounded open\todo{MV: Weakly Lipschitz??} set with diameter $\cye{\diam(\Omega)} > 0$\todo{MV: Unifying the notation.}.

@@

We begin with introducing the Costabel-McIntosh kernel.
For any $\ell \in \{0,\dotsc,n\}$, we define the kernel $G_{\ell} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
\begin{equation}\label{math:mainkernel}
  G_{\ell}(x,y) = \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} \vol(\Omega)^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
  .
\end{equation}
Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\ell)$, where \(1 \leq \ell \leq n\), 
we then define the integral operators
\begin{align*}
  \Poinc_{\ell} u(x) &= \int_{\Omega} G_{n-\ell+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
  \\
  \Bogov_{\ell} u(x) &= \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy.
\end{align*}
We call $\Poinc_{\ell}$ the Poincar\'e operator and $\Bogov_{\ell}$ the Bogovski\u{\i} operator.

We show that the integrals in the definition of $\Poinc_{\ell}$ and $\Bogov_{\ell}$ actually exist. 
In order to analyze the properties of the potential operators,
we first rewrite the Costabel-McIntosh kernel $G_{\ell}$.
Letting $x,y \in \bbR^n$ with $x \neq y$, we find 
\begin{align*}
    G_{\ell}(x,y) 
    &= 
    \int_{0}^{\infty} t^{n-\ell} (t+1)^{\ell-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
    \\
    &= 
    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-\ell+k} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
    \\
    &= 
    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{\ell-1-k} t^{n-\ell+\ell-1-k} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
    \\
    &= 
    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-k-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
    \\
    &= 
    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \int_{0}^{\infty} t^{n-k-1} \vol(\Omega)^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
    \\
    &= 
    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \, |x-y|^{k-n} \int_{0}^{\infty} r^{n-k-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
    .
\end{align*}
If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq \diam(\Omega)$, which gives 
\begin{align*}
    G_{\ell}(x,y) 
    &= 
    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_{0}^{\diam(\Omega)} r^{n-k-1} \,dr 
    \\
    &= 
    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \frac{ \diam(\Omega)^{n-k} }{n-k}.
\end{align*}
We are now in a position to show that the potentials are bounded with respect to Lebesgue norms.

@@

We begin with the Poincar\'e operator. 
Let $B_{\diam(\Omega)}(0)$ be the $n$-dimensional ball centered at the origin.
Suppose that $u \in L^{\infty}\Alt^{\ell}(\Omega)$ with $1 \leq \ell \leq n$.
We pointwise estimate $\Poinc_{\ell} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
\begin{align*}
    \left| \Poinc_{\ell} u(x) \right|
    &=
    \left| 
        \int_{\Omega} G_{n-\ell+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
%     \\&\leq 
%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{(n-\ell+1)-1}\tbinom{(n-\ell+1)-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
    \\&\leq 
    \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{ n-\ell }\tbinom{ n-\ell }{k} \frac{ \diam(\Omega)^{n-k} }{n-k} |x-y|^{k+1-n} \chi_{B_{\diam(\Omega)}(0)}(x-y) |u(y)| \,dy
    .
\end{align*}
We recall the radial integrals 
\begin{align*}
    \int_{B_{\diam(\Omega)}(0)} |z|^{k+1-n} \,dz
    &
    =
    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{k+1-n} r^{n-1} \,dr
    \\&
    =
    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{k} \,dr
    =
    \vol_{n-1}(S_1) \frac{\diam(\Omega)^{k+1}}{k+1}
    ,
\end{align*}
where $S_1 \subseteq \bbR^{n}$ stands for the unit sphere of dimension $n-1$. 
We compute 
\begin{align}
    &
    \int_{\bbR^{n}} \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{k+1-n} \,dz
    \\&
    =
    \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \int_{B_{\diam(\Omega)}(0)} |z|^{k+1-n} \,dz
    \\&
    =
    \vol_{n-1}(S_1) \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \frac{\diam(\Omega)^{k+1}}{k+1}
    %\\&
    =
    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{k=0}^{n-\ell} \frac{ \tbinom{n-\ell}{k} }{ (n-k)(k+1) } }_{ =: A_{\Poinc}(n,\ell) \leq 2^{n-\ell}}
    \label{equation:A_Poinc}
    .
\end{align}
Here, $A_{\Poinc}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
and which is bounded by $2^{n-\ell}$. 
In particular, the integral $\Poinc_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
So the convolution of $u$ is taken against an integrable function. 
Young's convolution inequality now implies: 
\begin{align*}
    \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
    &
    \leq 
    \vol_{n-1}(S_1) A_{\Poinc}(n,\ell) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    \\&
    \leq 
    n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
We have assumed so far that $u \in L^{\infty}\Alt^{\ell}(\Omega)$. 
Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
\begin{gather*}
    \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}\Alt^{\ell-1}(\bbR^n).
\end{gather*}
% Its operator norm is bounded by $n A_{\Poinc}(n,\ell) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
%

@@

    \Poinc_{\ell,a} u(x) 

@@

    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;

@@

    \sum_{\sigma \in \Sigma(k,n)}

@@

    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} \,dt 
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}

@@

    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 

@@

    \cartan \Poinc_{\ell,a} u(x) 

@@

    \ell
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}

@@

    t^{\ell-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 

@@

    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k} \sum_{j=1}^{n}

@@

    t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 

@@

    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}

@@

    \Poinc_{\ell+1,a} \cartan u(x)

@@

    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 

@@

    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt (x-a)_{j}

@@

    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 

@@

    \cartan \Poinc_{\ell,a} u(x)
    \Poinc_{\ell+1,a} \cartan u(x)
    \ell
    \sum_{\sigma \in \Sigma(k,n)} \sum_{i=1}^{k}

@@

    \sum_{\sigma \in \Sigma(k,n)} \sum_{j=1}^{n}
    \int_{0}^{1} t^{\ell} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}

>>>>

\subsection{A triangulation or a simplicial complex}

@@

A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation} if it satisfies the following conditions: 
(i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
% (i) every subsimplex of any simplex in $\calT$ is itself part of $\calT$, and (ii) the intersection between any two simplices $T, T' \in \calT$ is either empty or a shared subsimplex of both $T$ and $T'$. 
We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) \cye{and simply ``simplicial meshes'' in the finite element literature}.} 
We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is \sout{defined as} the union 
\begin{align*}
    \underlying{\calT} := \bigcup_{ T \in \calT } T
    .
\end{align*}
We call any set triangulable if it is the underlying set of some triangulation. 
\\

@@

We introduce a specific notion of connectivity when we are given an $n$-dimensional simplicial complex $\calT$. 
We call two $n$-dimensional simplices $S, S' \in \calT$ \emph{face-neighboring} if $S \cap S'$ is a common face of both of them. 
We call $n$-simplices $S,S' \in \calT$ \emph{face-connected in $\calT$} if there exists a sequence $S=S_0,S_1,\dots,S_m=S' \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$. 
We call such a sequence a \emph{face path} from $S$ to $S'$ in $\calT$. 
Clearly, face-connected in $\calT$ is an equivalence relation among simplices. 
A \emph{face-connected component} of $\calT$ is an equivalence class under this equivalence relation, 
and we call $\calT$ \emph{face-connected} if it has only one face-connected component.

@@

@@

We are interested in transformations of Sobolev tensor fields from one domain onto another. 
Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
The pullback of $u \in W^{p}\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
\begin{align} \label{equation:pullback}
    \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
    := 
    u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
\end{align}
for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^{p}\Alt^{k}(\Omega)$.
We cite an explicit transformation estimate~\cite{licht2019smoothed}.

\begin{proposition} \label{proposition:pullbackestimate}
 Let $\phi : \Omega \rightarrow \Omega'$ be a bi-Lipschitz mapping between open sets $\Omega, \Omega' \subseteq \bbR^{n}$.
 Let $p \in [1,\infty]$ and $u \in L^{p}\Lambda^{k}(\Omega)$. 
 Then 
 \begin{align}\label{math:pullbackestimate}
  \begin{split}
  \| \phi^{\ast} u \|_{L^{p}\Lambda^{k}(\Omega)}
  &\leq 
  \| \Jacobian \phi \|^{k}_{L^{\infty}(\Omega)}
  \| \det\Jacobian \phi^{-1} \|^{\frac{1}{p}}_{L^{\infty}(\Omega')}
  \| u \|_{L^{p}\Lambda^{k}(\Omega')}
  .
  \end{split}
 \end{align}
\end{proposition}
\notice{MWL:I have simplified the statement to what is needed later.}

@@

We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
We already know the optimal constants for the gradient operator over convex domains,
and we know bounds for the Poincar\'e--Friedrichs constants for the entire $L^{2}$ de~Rham complex. 
We are not aware of such bounds for the case of the $L^{p}$ de~Rham complex when $1 \leq p \leq \infty$.

\mwl{We \cye{now give} bounds for Poincar\'e--Friedrichs constants for the exterior derivative over convex domains\cye{, in} two special cases:}
For that reason, we bound the norms of regularized potential operators for the exterior derivative over convex domains.
We solve this for two special cases: 
either the $L^{p}$ de~Rham complex without boundary conditions, 
or the $L^{p}$ de~Rham with full boundary conditions. 
either the $L^{p}$ de~Rham complex without boundary conditions, 
or the $L^{p}$ de~Rham with full boundary conditions. 
The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
who analyze them as pseudo-differential operators over domains star-shaped with respect to a ball. 
% 
In comparison to their extensive work, our discussion is more modest:
we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
However, our purpose are explicit bounds for the operator norms, giving the Poincar\'e--Friedrichs constants.

%\mwl{In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.}
Let $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.
\todo{MV: Discussion already in the introduction, or in Remark~\ref{remark:reg_Poinc_Bog}}:

@@

We begin with introducing the Costabel-McIntosh kernel.
For any $\mia \in \{0,\dotsc,n\}$, we define the kernel $\calG_{\mia} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
\begin{equation}\label{math:mainkernel}
  \calG_{\mia}(x,y) = \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} \vol(\Omega)^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
  ,
\end{equation}
where $\chi_{\Omega} : \Omega \rightarrow \{0,1\}$ denotes the characteristic function of the domain $\Omega$.
Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\mia)$, where \(1 \leq \mia \leq n\), 
we then define the integral operators
\begin{align*}
  \Poinc_{\mia} u(x) &= \int_{\Omega} \calG_{n-\mia+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
  \\
  \Bogov_{\mia} u(x) &= \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy.
\end{align*}
We call $\Poinc_{\mia}$ the Poincar\'e operator and $\Bogov_{\mia}$ the Bogovski\u{\i} operator.

We show that the integrals in the definition of $\Poinc_{\mia}$ and $\Bogov_{\mia}$ actually exist. 
In order to analyze the properties of the potential operators,
we first rewrite the Costabel-McIntosh kernel $\calG_{\mia}$.
Letting $x,y \in \bbR^n$ with $x \neq y$, we find 
\begin{align*}
    \calG_{\mia}(x,y) 
    &= 
    \int_{0}^{\infty} t^{n-\mia} (t+1)^{\mia-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
    \\
    &= 
    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} t^{n-\mia+\jeza} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
    \\
    &= 
    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\mia-1-\jeza} t^{n-\mia+\mia-1-\jeza} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
    \\
    &= 
    \int_{0}^{\infty} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} t^{n-\jeza-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
    \\
    &= 
    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \int_{0}^{\infty} t^{n-\jeza-1} \vol(\Omega)^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
    \\
    &= 
    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \, |x-y|^{\jeza-n} \int_{0}^{\infty} r^{n-\jeza-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
    .
\end{align*}
If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq \diam(\Omega)$, which gives 
\begin{align*}
    \calG_{\mia}(x,y) 
    &= 
    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} |x-y|^{\jeza-n} \int_{0}^{\diam(\Omega)} r^{n-\jeza-1} \,dr 
    \\
    &= 
    \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} |x-y|^{\jeza-n} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza}.
\end{align*}
We are now in a position to show that the potentials are bounded with respect to Lebesgue norms.

@@

We begin with the Poincar\'e operator. 
Let $B_{\diam(\Omega)}(0)$ be the $n$-dimensional ball centered at the origin.
Suppose that $u \in L^{\infty}\Alt^{\mia}(\Omega)$ with $1 \leq \mia \leq n$.
We pointwise estimate $\Poinc_{\mia} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
\begin{align*}
    \left| \Poinc_{\mia} u(x) \right|
    &=
    \left| 
        \int_{\Omega} \calG_{n-\mia+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
%     \\&\leq 
%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{(n-\mia+1)-1}\tbinom{(n-\mia+1)-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
    \\&\leq 
    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{ n-\mia }\tbinom{ n-\mia }{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} \chi_{B_{\diam(\Omega)}(0)}(x-y) |u(y)| \,dy
    .
\end{align*}
We recall the radial integrals 
\begin{align*}
    \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
    &
    =
    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} \,dr
    \\&
    =
    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} \,dr
    =
    \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
    ,
\end{align*}
where $S_1 \subseteq \bbR^{n}$ stands for the unit sphere of dimension $n-1$. 
We compute 
\begin{align}
    &
    \int_{\bbR^{n}} \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
    \\&
    =
    \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
    \\&
    =
    \vol_{n-1}(S_1) \sum_{\jeza=0}^{n-\mia} \tbinom{n-\mia}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
    %\\&
    =
    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{n-\mia} \frac{ \tbinom{n-\mia}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: A_{\Poinc}(n,\mia) \leq 2^{n-\mia}}
    \label{equation:A_Poinc}
    .
\end{align}
Here, $A_{\Poinc}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ 
and which is bounded by $2^{n-\mia}$. 
In particular, the integral $\Poinc_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
So the convolution of $u$ is taken against an integrable function. 
Young's convolution inequality now implies: 
\begin{align*}
    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
    &
    \leq 
    \vol_{n-1}(S_1) A_{\Poinc}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    \\&
    \leq 
    n A_{\Poinc}(n,\mia) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
We have assumed so far that $u \in L^{\infty}\Alt^{\mia}(\Omega)$. 
Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
\begin{gather*}
    \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
\end{gather*}
% Its operator norm is bounded by $n A_{\Poinc}(n,\mia) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
%

@@

    \Poinc_{\mia,a} u(x) 

@@

    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da\;

@@

    \sum_{\sigma \in \Sigma(\mia,n)}

@@

    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \cartanx^{\sigma} \,dt 
    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}

@@

    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{\sigma-\sigma(i)} \,dt 

@@

    \cartan \Poinc_{\mia,a} u(x) 

@@

    \mia
    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}

@@

    t^{\mia-1} u_{\sigma}\left(a+t(x-a)\right) \,\cartanx^{\sigma-\sigma(i)} \,dt 

@@

    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia} \sum_{j=1}^{n}

@@

    t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) (-1)^{i-1} (x-a)_{\sigma(i) } \,\cartanx^{j} \wedge \cartanx^{\sigma-\sigma(i)} \,dt 

@@

    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}

@@

    \Poinc_{\mia+1,a} \cartan u(x)

@@

    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 

@@

    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt (x-a)_{j}

@@

    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt 

@@

    \cartan \Poinc_{\mia,a} u(x)
    \Poinc_{\mia+1,a} \cartan u(x)
    \mia
    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{i=1}^{\mia}

@@

    \sum_{\sigma \in \Sigma(\mia,n)} \sum_{j=1}^{n}
    \int_{0}^{1} t^{\mia} \frac{ \partial u_{\sigma} }{\partial x_{j}}\left(a+t(x-a)\right) \,dt \,(x-a)_{j} \,\cartanx^{\sigma}
